Exact asymptotic expressions for local clustering in hyperbolic random graphs

### 2018-10-18 clustering_infinite_model.tex
cleaned up proof of Theorem 1.5 and realigned formulas in section 4.5

Using the above equation and the transformation of variables $z = \xi_{\alpha,\nu}e^{\frac{y}{2}}$, we compute
\begin{align*}
	\int_0^\infty \rho(y,k) e^{-\alpha y} \, dy 
    &= \frac{1}{\Gamma(k+1)} \int_0^\infty \left(\xi_{\alpha,\nu} e^{\frac{y}{2}}\right)^k 
    	e^{-\xi_{\alpha,\nu} e^{\frac{y}{2}}} e^{-\alpha y} \, dy\\
    &= \frac{(\xi_{\alpha,\nu})^{2\alpha}}{\Gamma(k+1)} \int_0^\infty 
    	\left(\xi_{\alpha,\nu} e^{\frac{y}{2}}\right)^{k - 2\alpha} e^{-\xi_{\alpha,\nu} e^{\frac{y}{2}}}
        \, dy\\
    &= \frac{(\xi_{\alpha,\nu})^{2\alpha}}{\Gamma(k+1)} \int_{\xi_{\alpha,\nu}}^{\infty} 
    	z^{k-2\alpha} e^{-z} \, dz\\
    &= (\xi_{\alpha,\nu})^{2\alpha}\frac{\Gamma(k-2\alpha)}{\Gamma(k+1)}
    	\left(1 - \frac{\gamma(k-2\alpha, \xi_{\alpha,\nu})}{\Gamma(k - 2\alpha)}\right),
        \numberthis \label{eq:degree_distribution_P}
\end{align*}
where $\Gamma$ denotes the Gamma-function and $\gamma$ the incomplete Gamma-function.

Thus we deduce that, as $k \to \infty$,
\begin{equation}\label{eq:degree_distribution_P_asymptotics}
	\Prob{D_\Pcal = k} = \int_0^\infty \rho_{y}(k) e^{-\alpha y} \, dy \sim (\xi_{\alpha,\nu})^{2\alpha} k^{-(2\alpha + 1)}.
\end{equation}

By a similar computation we have the following result, which will be useful later on. For any $\beta > 0$,
\begin{equation}\label{eq:general_integral_rho_y_k}
	\int_0^\infty e^{\beta y} \rho_y(k) e^{-\alpha y} \, dy
    = \left(\xi_{\alpha,\nu}\right)^{2(\beta + \alpha)} \frac{\Gamma(k - 2(\beta + \alpha))}{\Gamma(k+1)}
    	\left(1 - \frac{\gamma(k - 2(\beta + \alpha), \xi_{\alpha,\nu})}{\Gamma(k - 2(\beta + \alpha))}\right).
\end{equation}

@@

\begin{proposition}[Asymptotic behavior of $\Delta_\Pcal(y)$]\label{prop:asymptotics_Delta_y_P}
Let $\alpha > \frac{1}{2}$, $\nu > 0$ and $C_\alpha$ as defined in \eqref{eq:def_C_alpha}. Then there are three, eventually decreasing, functions $\varepsilon_i : \R_+ \mapsto \R$, $i = 1,2,3$, satisfying
\[
	\lim_{y \to \infty} \varepsilon_i(y) = 0, 
\]
such that 
\begin{enumerate}
\item for $\frac{1}{2} < \alpha < \frac{3}{4}$,
\[
	\Delta_{\Pcal}(y) = e^{-\frac{y}{2}(4\alpha - 2)} C_\alpha (1 + \varepsilon_1(y)),
\]
\item for $\alpha = \frac{3}{4}$,
\[
	\Delta_\Pcal(y) = \log\left(\frac{y}{2}\right)e^{-\frac{y}{2}}(1 + \varepsilon_2(y)),
\]
\item and for $\alpha > \frac{3}{4}$,
\[
	\Delta_{\Pcal}(y) = e^{-\frac{y}{2}} \frac{\alpha - \frac{1}{2}}{\alpha - \frac{3}{4}} (1 + \varepsilon_3(y)).
\]
\end{enumerate}
\end{proposition}

@@

\PvdH{Include concentration argument in this proof.}
We only give the proof for the case $\frac{1}{2} < \alpha < \frac{3}{4}$. The proofs for the other two cases are similar. Let $\varepsilon_1(y)$ be defined as in Proposition \ref{prop:asymptotics_Delta_y_P} and define
\[
	\xi_1(k_n) = \int_0^{\infty} \varepsilon_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho_{y}(k_n) e^{-\alpha y} \, dy
\]
Then we have that
\[
	\int_0^{\infty} \Delta_{\mathcal{P}}(y) \rho_{y}(k_n) e^{-\alpha y} \, dy
	= C_\alpha \int_0^{\infty} e^{-(4\alpha - 2)\frac{y}{2}} \rho_{y}(k_n) e^{-\alpha y} \, dy + \xi_1(k_n).
\]

Using \eqref{eq:general_integral_rho_y_k} with $\beta = 2\alpha - 1$ yields
\[
	\int_0^{\infty} e^{-(4\alpha - 2)\frac{y}{2}} \rho_{y}(k_n) e^{-\alpha y} \, dy 
    = 2\xi^{6\alpha - 2} \frac{\Gamma(k_n-(6\alpha-2)}{\Gamma(k_n+1)}
	\left(1 - \frac{\gamma(k_n - (6\alpha - 2), \xi)}{\Gamma(k_n - (6\alpha-2))}\right).
\]
Since 
\[
	\lim_{n \to \infty} \frac{\gamma(k_n - 2\alpha, \xi)}{\Gamma(k_n - 2\alpha)} = 0,
\]
and $\Gamma(k_n - t)/\Gamma(k_n + 1) \sim k_n^{-(t+1)}$ as $n \to \infty$,
it follows that, as $n \to \infty$,
\begin{align*}
	c_\infty(k_n) \sim C_\alpha \xi^{4\alpha - 2} \frac{k_n^{-(6\alpha - 1)}}{k_n^{-(2\alpha - 1)}}
	+ \frac{\xi^{-2\alpha}\eta_1(k_n)}{2 k_n^{-(2\alpha - 1)}}
	\sim C_\alpha \xi^{4\alpha - 2} k_n^{-4\alpha + 2} 
    + \frac{\xi^{-2\alpha}\eta_1(k_n)}{2 k_n^{-(2\alpha - 1)}}.
\end{align*}
Hence, to prove the result it is enough to show that
\[
	\lim_{n \to \infty} k_n^{6\alpha - 1}\xi_1(k_n) = 0.
\]
For this let $0 < \varepsilon < 1$, define $a_n = 2\log((1-\varepsilon)k_n)$ and split the integral into two pieces
\begin{align*}
	\xi_1(k_n) &= \int_0^{\infty} \varepsilon_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho_{y}(k_n) e^{-\alpha y} \, dy\\
	&= \int_0^{a_n} \varepsilon_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho_{y}(k_n) e^{-\alpha y} \, dy\\
	&\hspace{10pt}+ \int_{a_n}^{\infty} \varepsilon_1(y) e^{-(4\alpha - 2)\frac{y}{2}} 
    	\rho_{y}(k_n) e^{-\alpha y} \, dy.
\end{align*} 
For the first integral we use that
\[
	k_n^{6\alpha - 1}\rho_{a_n}(k_n) = O\left(\frac{k_n^{6\alpha - 1 + (1-\varepsilon)k_n}}{k_n!} e^{-(1-\varepsilon)k_n}\right) = o(1),
\]
so that
\begin{align*}
	&\hspace{-30pt}\lim_{n \to \infty} k_n^{6\alpha - 1} \int_0^{a_n} \varepsilon_1(y) e^{-(4\alpha - 2)\frac{y}{2}} 
    	\rho_{y}(k_n) e^{-\alpha y} \, dy\\
	&\le \lim_{n \to \infty} \left(\max_{0 \le y \le a_n} \varepsilon_1(y)\right) k_n^{6\alpha - 1} 
    	\rho_{a_n}(k_n) \int_0^\infty e^{-\alpha y} \, dy = 0.
\end{align*}
For the second integral we first note that due to \eqref{eq:asymptotics_clustering_integral}
\[
	\int_0^\infty e^{-(4\alpha - 2)\frac{y}{2}} \rho_{y}(k_n) e^{-\alpha y} \, dy \sim k_n^{-(6\alpha - 1)}.
\] 
Therefore, using that $\varepsilon_1(y)$ is eventually decreasing and $\lim_{n \to \infty} \varepsilon_1(a_n) = 0$, we obtain
\begin{align*}
	&\hspace{-30pt}\lim_{n \to \infty} k_n^{6\alpha - 1} \int_{a_n}^{\infty} \varepsilon_1(y) 
    	e^{-(4\alpha - 2)\frac{y}{2}} \rho_{y}(k_n) e^{-\alpha y} \, dy\\
	&\le \lim_{n \to \infty} \varepsilon_1(a_n) k_n^{6\alpha - 1} \int_0^\infty 
    	e^{-(4\alpha - 2)\frac{y}{2}} \rho_{y}(k_n) e^{-\alpha y} \, dy = 0,
\end{align*}
which finishes the proof.
\end{proof}

@@

\begin{figure}
\centering
\begin{tikzpicture}[scale=0.9]

	\draw node at (0,3.5) {\begin{minipage}{5cm}
		\begin{center}
		\begin{align*}
			&\text{I) } e^{\frac{y_0 + y_1}{2}} < e^{\frac{y_1 + y_2}{2}} - e^{\frac{y_0 + y_2}{2}} \text{ or}\\
			&\text{II) } 0 \le x_1 \le e^{\frac{y_1 + y_2}{2}} - e^{\frac{y_0 + y_2}{2}}
		\end{align*}
		\end{center}
	\end{minipage}};

	\draw[thick,red] (-2,1) -- (2,1);
	\draw[thick] (-2,0.8) -- (-2,1.2);
	\draw[thick] (2,0.8) -- (2,1.2);
	\draw node at (-2,1.5) {$-e^{\frac{y_0 + y_2}{2}}$};
	\draw node at (2,1.5) {$e^{\frac{y_0 + y_2}{2}}$};

	\draw[thick] (-3,0) -- (3,0);
	\draw[thick,red] (-2,0) -- (2,0);
	\draw[thick,red] (-2,-0.2) -- (-2,0.2);
	\draw[thick,red] (2,-0.2) -- (2,0.2);
	\draw[thick] (-3,-0.2) -- (-3,0.2);
	\draw[thick] (3,-0.2) -- (3,0.2);
	\draw node at (-3,-0.5) {$x_1 - e^{\frac{y_1 + y_2}{2}}$};
	\draw node at (3,-0.5) {$x_1 + e^{\frac{y_1 + y_2}{2}}$};

\end{tikzpicture}
\begin{tikzpicture}[scale=0.9]

	\draw node at (0,3.5) {\begin{minipage}{5cm}
		\begin{center}
			$x_1 > e^{\frac{y_1 + y_2}{2}} - e^{\frac{y_0 + y_2}{2}}$
		\end{center}
	\end{minipage}};

	\draw[thick] (-2,1) -- (2,1);
	\draw[thick,red] (-1.5,1) -- (2,1);
	\draw[thick] (-2,0.8) -- (-2,1.2);
	\draw[thick] (2,0.8) -- (2,1.2);
	\draw[thick,red] (-1.5,0.8) -- (-1.5,1.2);
	\draw node at (-2,1.5) {$-e^{\frac{y_0 + y_2}{2}}$};
	\draw node at (2,1.5) {$e^{\frac{y_0 + y_2}{2}}$};

	\draw[thick] (-1.5,0) -- (3,0);
	\draw[thick,red] (-1.5,0) -- (2,0);
	\draw[thick,red] (2,-0.2) -- (2,0.2);
	\draw[thick] (-1.5,-0.2) -- (-1.5,0.2);
	\draw[thick] (3,-0.2) -- (3,0.2);
	\draw node at (-1.5,-0.5) {$x_1 - e^{\frac{y_1 + y_2}{2}}$};
	\draw node at (3,-0.5) {$x_1 + e^{\frac{y_1 + y_2}{2}}$};

\end{tikzpicture}
\end{figure}

@@

Next we compute $J_{a,b,c}(z_0)$.
\begin{align*}
	J_{a,b,c} 
	&= z_0^a \int_{z_0/2}^{z_0}\int_{z_0-z_1}^{z_1} z_1^{b+2\alpha-2} z_2^{c+2\alpha-2} {\dd}z_2{\dd}z_1
		= z_0^a \int_{z_0/2}^{z_0} z_1^{b+2\alpha-2} \left[ \frac{ z_2^{c+2\alpha-1} }{ c+2\alpha-1 } \right]_{z_0-z_1}^{z_1} \dd z_1\\
	&= \frac{z_0^a}{c+2\alpha-1} \cdot \left( \int_{z_0/2}^{z_0} z_1^{b+c+4\alpha-3} {\dd}z_1
	   - \int_{z_0/2}^{z_0} z_1^{b+2\alpha-2} (z_0-z_1)^{c+2\alpha-1} {\dd}z_1 \right) \\
	&= \frac{z_0^{a+b+c+4\alpha-2}(1-(1/2)^{b+c+4\alpha-2})}{(c+2\alpha-1)(b+c+4\alpha-2)} 
		- \frac{z_0^{a+b+c+4\alpha-3}}{c+2\alpha-1} \int_{z_0/2}^{z_0}  \left(z_1/z_0\right)^{b+2\alpha-2} 
	    \left(1-(z_1/z_0)\right)^{c+2\alpha-1} {\dd}z_1\\
	&= \frac{z_0^{4\alpha-2}(1-(1/2)^{b+c+4\alpha-2})}{(c+2\alpha-1)(b+c+4\alpha-2)} 
		- \frac{z_0^{4\alpha-2}}{c+2\alpha-1}
	   \int_{1/2}^1  u^{b+2\alpha-2}(1-u)^{c+2\alpha-1} {\dd} u \\
	&= \frac{z_0^{4\alpha-2}(1-(1/2)^{b+c+4\alpha-2})}{(c+2\alpha-1)(b+c+4\alpha-2)} 
		- \frac{z_0^{4\alpha-2}}{c+2\alpha-1} B^-(1/2;c+2\alpha, b+2\alpha-1),
\end{align*}
where we've used the substitution $u := z_1/z_0$ giving $z_0 {\dd} u = {\dd} z_1$ in the penultimate line and
$B^-$ denotes the (lower) incomplete beta-function. Note that since $c \geq -1$, $-a \in \{0,-1,-2\}$ and by our assumption $\alpha \not \in \{\frac{3}{4}\}$, the denominators that occur during the integration are all non-zero.

@@

To deal with $I_{22}(y_0)$ we consider the integral function
\[
	J_{a,b,c}^\prime(z_0) := z_0^a \int_{{1>z_1>\max(z_0,z_2); z_0,z_2>0}\atop{z_1 < z_0+z_2}} z_1^{b+2\alpha-2} z_2^{c+2\alpha-2} {\dd}z_2{\dd}z_1
\]
and note that
\begin{equation}\label{eq:Delta_P_computation_I22_J}
	I_{2,2}(y_0) = \frac{1}{4}\left(J_{0,-1,1}^\prime(z_0) + J_{2,-1,-1}^\prime(z_0)
	+ J_{0,1,-1}^\prime(z_0) + 2J_{1,-1,0}^\prime(z_0) - 2J_{0,0,0}^\prime(z_0) - 2J_{1,0,-1}^\prime(z_0)\right)
\end{equation}

@@

\PvdH{Realign formulas to fit them on page.}

>>>>

Using the above equation and the transformation of variables $z = \xi_{\alpha,\nu}e^{\frac{y}{2}}$, we compute
\begin{align*}
	\int_0^\infty \rho(y,k) e^{-\alpha y} \, dy 
    &= \frac{1}{\Gamma(k+1)} \int_0^\infty \left(\xi_{\alpha,\nu} e^{\frac{y}{2}}\right)^k 
    	e^{-\xi_{\alpha,\nu} e^{\frac{y}{2}}} e^{-\alpha y} \, dy\\
    &= \frac{(\xi_{\alpha,\nu})^{2\alpha}}{\Gamma(k+1)} \int_0^\infty 
    	\left(\xi_{\alpha,\nu} e^{\frac{y}{2}}\right)^{k - 2\alpha} e^{-\xi_{\alpha,\nu} e^{\frac{y}{2}}}
        \, dy\\
    &= \frac{(\xi_{\alpha,\nu})^{2\alpha}}{\Gamma(k+1)} \int_{\xi_{\alpha,\nu}}^{\infty} 
    	z^{k-2\alpha} e^{-z} \, dz\\
    &= (\xi_{\alpha,\nu})^{2\alpha}\frac{\Gamma(k-2\alpha)}{\Gamma(k+1)}
    	\left(1 - \frac{\Gamma^{-}(k-2\alpha, \xi_{\alpha,\nu})}{\Gamma(k - 2\alpha)}\right),
        \numberthis \label{eq:degree_distribution_P}
\end{align*}
where we recall that $\Gamma$ denotes the Gamma-function and $\Gamma^{-1}$ the lower-incomplete Gamma-function.

Since $\Gamma^{-}(k-2\alpha, \xi_{\alpha,\nu})\Gamma(k - 2\alpha) \to 0$ \PvdH{Find reference.} and $\Gamma(k-t)/\Gamma(k+1) \sim k^{-(t+1)}$ as $k \to \infty$ we deduce that
\begin{equation}\label{eq:degree_distribution_P_asymptotics}
	\Prob{D_\Pcal = k} = \int_0^\infty \rho_{y}(k) e^{-\alpha y} \, dy \sim (\xi_{\alpha,\nu})^{2\alpha} k^{-(2\alpha + 1)}.
\end{equation}

By a similar computation we have the following result, which will be useful later on. For any $\beta > 0$, as $k \to \infty$
\begin{equation}\label{eq:general_integral_rho_y_k}
	\int_0^\infty e^{\beta y} \rho_y(k) e^{-\alpha y} \, dy
    \sim \left(\xi_{\alpha,\nu}\right)^{2(\beta + \alpha)} k^{-2(\beta + \alpha)-1}.
\end{equation}

@@

\begin{proposition}[Asymptotic behavior of $\Delta_\Pcal(y)$]\label{prop:asymptotics_Delta_y_P}
Let $\alpha > \frac{1}{2}$, $\nu > 0$ and $C_\alpha$ as defined in \eqref{eq:def_C_alpha}. Then there are three, eventually decreasing, functions $\varphi_i : \R_+ \mapsto \R$, $i = 1,2,3$, satisfying
\[
	\lim_{y \to \infty} \varphi_i(y) = 0, 
\]
such that 
\begin{enumerate}
\item for $\frac{1}{2} < \alpha < \frac{3}{4}$,
\[
	\Delta_{\Pcal}(y) = e^{-\frac{y}{2}(4\alpha - 2)} C_\alpha (1 + \varphi_1(y)),
\]
\item for $\alpha = \frac{3}{4}$,
\[
	\Delta_\Pcal(y) = \log\left(\frac{y}{2}\right)e^{-\frac{y}{2}}(1 + \varphi_2(y)),
\]
\item and for $\alpha > \frac{3}{4}$,
\[
	\Delta_{\Pcal}(y) = e^{-\frac{y}{2}} \frac{\alpha - \frac{1}{2}}{\alpha - \frac{3}{4}} (1 + \varphi_3(y)).
\]
\end{enumerate}
\end{proposition}

@@

We only give the proof for the case $\frac{1}{2} < \alpha < \frac{3}{4}$. The proofs for the other two cases are similar. Let $\varphi_1(y)$ be defined as in Proposition \ref{prop:asymptotics_Delta_y_P} and define
\[
	\epsilon_1(k) = \int_0^{\infty} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) e^{-\alpha y} \dd y
\]
Then we have that
\[
	\int_0^{\infty} \Delta_{\mathcal{P}}(y) \rho(y,k) e^{-\alpha y} \dd y
	= C_\alpha \int_0^{\infty} e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) e^{-\alpha y} \dd y + \epsilon_1(k).
\]

Using \eqref{eq:general_integral_rho_y_k} with $\beta = 2\alpha - 1$ yields,
\begin{equation}\label{eq:asymptotics_clustering_integral}
	\int_0^{\infty} e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) e^{-\alpha y} \dd y 
	\sim \xi_{\alpha,\nu}^{6\alpha - 2} k^{-(6\alpha - 1)},
\end{equation}
as $k \to \infty$. Therefore, by applying the asymptotic scaling for the denominator~\eqref{eq:degree_distribution_P_asymptotics} we get
\begin{align*}
	c_\infty(k) &= \frac{\int_0^{\infty} \Delta_{\mathcal{P}}(y) \rho(y,k) e^{-\alpha y} \dd y}
		{\int_0^\infty \rho_{y}(k) e^{-\alpha y} \dd y} \\
	&\sim C_\alpha \xi_{\alpha,\nu}^{4\alpha - 2} \frac{k^{-(6\alpha - 1)}}{k^{-(2\alpha - 1)}}
	+ \frac{\epsilon_1(k)}{\xi_{\alpha,\nu}^{2\alpha} k^{-(2\alpha - 1)}}\\
	&= C_\alpha \xi_{\alpha,\nu}^{4\alpha - 2} k^{-4\alpha + 2} 
    + \xi_{\alpha,\nu}^{-2\alpha} k^{2\alpha - 1}\epsilon_1(k).
\end{align*}
Hence, to prove the result it is enough to show that
\[
	\lim_{k \to \infty} k^{6\alpha - 3}\epsilon_1(k) = 0.
\]
For this we fix $0 < \varphi < 1$, define $a(k) = 2\log((1-\varphi)k)$ and split the integral into two pieces
\begin{align*}
	\epsilon_1(k) &= \int_0^{\infty} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) e^{-\alpha y} \dd y\\
	&= \int_0^{a(k)} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) e^{-\alpha y} \dd y\\
	&\hspace{10pt}+ \int_{a(k)}^{\infty} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} 
    	\rho(y,k) e^{-\alpha y} \dd y.
\end{align*} 
For the first integral we use that $\rho(y,k)$ is increasing on $[0,a(k)]$ and
\[
	k^{6\alpha - 3}\rho(a(k),k) = O\left(\frac{k^{6\alpha - 3 + (1-\varphi)k}}{k!} e^{-(1-\varphi)k}\right) = o(1),
\]
to obtain
\begin{align*}
	&\hspace{-30pt}\lim_{k \to \infty} k^{6\alpha - 3} \int_0^{a_n} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} 
    	\rho(y,k) e^{-\alpha y} \dd y\\
	&\le \lim_{n \to \infty} \left(\max_{0 \le y \le a(k)} \varphi_1(y)\right) k^{6\alpha - 1} 
    	\rho(a(k), k) \int_0^\infty e^{-\alpha y} \dd y = 0.
\end{align*}
For the second integral we first note that due to \eqref{eq:asymptotics_clustering_integral}
\[
	\int_0^\infty e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) e^{-\alpha y} \dd y = \bigT{k^{-(6\alpha - 1)}}.
\] 
Therefore, using that $\varphi_1(y)$ is eventually decreasing and $\lim_{k \to \infty} \varphi_1(a(k)) = 0$, we obtain
\begin{align*}
	&\hspace{-30pt}\lim_{k \to \infty} k^{6\alpha - 3} \int_{a(k)}^{\infty} \varphi_1(y) 
    	e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) e^{-\alpha y} \dd y\\
	&\le \lim_{k \to \infty} \varphi_1(a(k)) k^{6\alpha - 3} \int_0^\infty 
    	e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) e^{-\alpha y} \dd y = 0,
\end{align*}
which finishes the proof.
\end{proof}

@@

@@

Next we compute $J_{a,b,c}(z_0)$.
\begin{align*}
	J_{a,b,c} 
	&= z_0^a \int_{z_0/2}^{z_0}\int_{z_0-z_1}^{z_1} z_1^{b+2\alpha-2} z_2^{c+2\alpha-2} {\dd}z_2{\dd}z_1
		= z_0^a \int_{z_0/2}^{z_0} z_1^{b+2\alpha-2} \left[ \frac{ z_2^{c+2\alpha-1} }{ c+2\alpha-1 } \right]_{z_0-z_1}^{z_1} \dd z_1\\
	&= \frac{z_0^a}{c+2\alpha-1} \cdot \left( \int_{z_0/2}^{z_0} z_1^{b+c+4\alpha-3} \dd z_1
	   - \int_{z_0/2}^{z_0} z_1^{b+2\alpha-2} (z_0-z_1)^{c+2\alpha-1} {\dd}z_1 \right) \\
	&= \frac{z_0^{a+b+c+4\alpha-2}(1-(1/2)^{b+c+4\alpha-2})}{(c+2\alpha-1)(b+c+4\alpha-2)} \\
	&\hspace{10pt}- \frac{z_0^{a+b+c+4\alpha-3}}{c+2\alpha-1} \int_{z_0/2}^{z_0}  \left(z_1/z_0\right)^{b+2\alpha-2} 
	    \left(1-(z_1/z_0)\right)^{c+2\alpha-1} \dd z_1\\
	&= \frac{z_0^{4\alpha-2}(1-(1/2)^{b+c+4\alpha-2})}{(c+2\alpha-1)(b+c+4\alpha-2)} 
		- \frac{z_0^{4\alpha-2}}{c+2\alpha-1}
	   \int_{1/2}^1  u^{b+2\alpha-2}(1-u)^{c+2\alpha-1} \dd u \\
	&= \frac{z_0^{4\alpha-2}(1-(1/2)^{b+c+4\alpha-2})}{(c+2\alpha-1)(b+c+4\alpha-2)} 
		- \frac{z_0^{4\alpha-2}}{c+2\alpha-1} B^-(1/2;c+2\alpha, b+2\alpha-1),
\end{align*}
where we've used the substitution $u := z_1/z_0$ giving $z_0 {\dd} u = {\dd} z_1$ in the penultimate line and
$B^-$ denotes the (lower) incomplete beta-function. Note that since $c \geq -1$, $-a \in \{0,-1,-2\}$ and by our assumption $\alpha \not \in \{\frac{3}{4}\}$, the denominators that occur during the integration are all non-zero.

@@

To deal with $I_{22}(y_0)$ we consider the integral function
\[
	J_{a,b,c}^\prime(z_0) := z_0^a \int_{{1>z_1>\max(z_0,z_2); z_0,z_2>0}\atop{z_1 < z_0+z_2}} z_1^{b+2\alpha-2} z_2^{c+2\alpha-2} {\dd}z_2{\dd}z_1
\]
and note that
\begin{equation}\label{eq:Delta_P_computation_I22_J}
\begin{aligned}
		I_{2,2}(y_0) &= \frac{1}{4}\left(J_{0,-1,1}^\prime(z_0) + J_{2,-1,-1}^\prime(z_0)
		+ J_{0,1,-1}^\prime(z_0)\right) \\
		&\hspace{10pt}+ \frac{1}{2}\left( J_{1,-1,0}^\prime(z_0) - J_{0,0,0}^\prime(z_0) - J_{1,0,-1}^\prime(z_0)\right).
\end{aligned}
\end{equation}

@@
